A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2022-01-07 paper/elsarticle/elsarticle-template.tex
paper

\begin{figure}[ht]
    \centering
    \subfloat[\centering Projector calibration image (2D pattern position detections overlain).]{{\includegraphics[height=3.1cm]{images/detections.png} }}
    \qquad
    \subfloat[\centering Corresponding 3D positions for use in projector calibration (red, in scene plane).]{{\includegraphics[height=3.26cm]{images/2d3d.png}}}
    \caption{Obtaining the 3D positions of the 2D-3D correspondences for use in projector calibration. (a) For each target location, a projector calibration image is acquired from the viewpoint of the `downwards-facing' camera, containing a projected asymmetric circle pattern at the target location and a chessboard pattern placed on the floor nearby. Circle pattern center points and chessboard corners detected automatically (overlain for illustration). (b) Given a projector calibration image, the scene plane is recovered in the coordinate frame of the camera (black with up vector red) via spatial resection with respect to 2D-3D correspondences obtained using the chessboard pattern (blue); the 3D positions of the 2D-3D correspondences to be used in calibrating the projector (red, in scene plane) are obtained by intersection with the scene plane of the back-projections (rays, likewise gray) of the 2D center points of the circle pattern detected in the image plane of the camera.} %The corresponding 2D positions are detected in the image of the asymmetric circles pattern image projected by the projector (not shown). The `downwards-facing' camera is shown relative to the scene plane in terms of its camera frustum (black, with up vector in red).
    \label{fig:2d}
\end{figure}

@@

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected.  We carry out this placement according to a small handful of steps. It is in accordance with the $X$- and $Y$-axes of the `downwards-facing' camera that we wish to place the $X$- and $Y$-axes of the augmentation; recognizing that a physical camera placed to face downwards is almost certain to not face downwards precisely, we first rotate the camera about its center of projection to align its optical axis\footnote{Strictly speaking, the optical axis is the back-projection of the principal point; in our usage, we understand it to refer to the ray through center of the image plane.} with the normal vector of the scene plane by applying the minimum arc-length rotation that relates the two, giving a \textit{virtual} camera facing directly downwards to the scene plane (cf.\ Figure~\ref{fig:virtualcam}). To obtain the virtual projector, we then (i) intersect the scene plane with the optical axis and rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and (ii) align the $X$- and $Y$-axes with those of the virtual camera. Finally, we (iii) translate along the scene plane's normal, in order to satisfy the desired metric projected image dimensions; the height $h$ [m] above the ground plane at which the virtual projector is to be placed if the image---with original image width of $w_\text{im}$ [px]---is to be projected to the scene plane with a metric width of $w$ [m] is given by
\begin{equation}
h = w \times f_\text{proj} / w_\text{im},
\end{equation}
where $f_\text{proj}$ [px] is the focal length of the projector. These three steps are illustrated in Figure~\ref{fig:virtualproj}. The resulting virtual projector is thus rendered fronto-parallel with the scene plane---enabling projection to the scene plane absent of projective distortions---and projects to the scene plane in the desired scale and with the the $X$- and $Y$-axes of the augmentation set in accordance with those of the `downwards-facing' camera. %\footnote{A physical camera placed to face downwards is almost certain to not face downwards precisely; in contrast, we align the virtual camera's optical axis exactly with the scene plane's normal vector, rendering it genuinely fronto-parallel with respect to the scene plane.}

@@

\begin{figure}
    \centering
    \includegraphics[height=4cm]{images/hans_undist_.pdf}
    \caption{Projection of the warped image from Figure \ref{fig:warp}(a) to corresponding target location at the upper-right corner of the floorspace, acquired by the `downwards-facing' camera. Note that besides correcting for projective distortions, the warp places the axes of the augmentation in accordance with the axes of the `downwards-facing' camera, and that the dimensions of the augmentation are in line with the desired target dimensions (50~cm~$\times$~31.25~cm). To provide context, the corners of the full projected image extent are projected to the floor in light green (emphasized with overlain dashed circles).}
    \label{fig:final_proj}
\end{figure}

@@

\begin{figure}
    \centering
    \subfloat[\centering Hardware setup (projector, steerable mirror system, camera).]{{\includegraphics[height=3.6cm]{images/system3_.pdf}}}
    \quad
    \subfloat[\centering Measurement for augmentation, using a steel rule and a digital angle gauge.]{{\includegraphics[height=3.6cm]{images/meas2_.pdf}}}
    \caption{Evaluation scenario. (a) Our hardware setup, comprised of a projector, a steerable mirror system, and a stereo camera, of which we used only the left view. (b) Example augmentation produced by projecting---to one of the 15 target locations across the floorspace considered in our evaluation, to the upper-left corner of our floorspace---an image warped using our approach. The digital angle gauge reads $89.6^\circ{}$ for the top-left corner, and the steel rule 49.9 cm for the bottom edge. Corners of the full projected image extent projected to the floor in light green to provide context. Note that blur has a minimal impact on the quality of the augmentation, and hence on the accuracy of the measurements.}
    \label{fig:eval}
\end{figure}

@@

\begin{table}[ht!]
\caption{Mean absolute error (MAE), minimum absolute error, and maximum absolute error in units of centimeters, with respect to the four sides (top, bottom, left, right) of the 15~augmentations produced using our approach for 15 target locations spread across the floorspace, respectively. Errors were computed against intended augmentation dimensions of 50~cm~$\times$~31.25~cm (i.e., 50~cm for top and bottom, 31.25~cm---rounded to 31.3~cm for the purposes of the computing the errors---for left and right).} %Note that absolute errors in no instance exceeded 1~cm for any side of any of the 15~augmentations.
\label{table:length}
\centering
{\small
\begin{tabularx}{7.4cm}{r p{1cm} p{1cm} p{1cm} p{1cm}}
\toprule
  & Top & Bottom & Left & Right \\
\midrule
MAE {\tiny[cm]} & 0.23 & 0.17 & 0.22 & 0.2 \\
Min AE {\tiny[cm]} & 0.0 & 0.0 & 0.0 & 0.0 \\
Max AE {\tiny[cm]} & 0.8 & 0.6 & 0.5 & 0.5 \\
\bottomrule
\end{tabularx}}
\end{table}

@@

\begin{table}[ht!]
\caption{Mean absolute error (MAE), minimum absolute error, and maximum absolute error in units of degrees, with respect to the top-left and bottom-right corners of the 15~augmentations produced using our approach for 15 target locations spread across the floorspace, respectively. Errors computed in terms of deviation from $90^\circ{}$.}
\label{table:angle}
\centering
{\small
\begin{tabularx}{6.75cm}{r p{1.95cm} p{1.95cm}}
\toprule
  & Top Left & Bottom Right \\
\midrule
MAE {\tiny[deg]} & 0.17 & 0.32 \\
Min AE {\tiny[deg]} & 0.0 & 0.0 \\
Max AE {\tiny[deg]} & 0.9 & 0.5 \\
\bottomrule
\end{tabularx}}
\end{table}

>>>>

\begin{figure}[ht]
    \centering
    \subfloat[\centering Projector calibration image (2D pattern position detections overlain).]{{\includegraphics[width=5.15cm]{images/detections_.png}}}
    \qquad
    \subfloat[\centering Corresponding 3D positions for use in projector calibration (red, in scene plane).]{{\includegraphics[height=3.5cm]{images/2d3d.png}}}
    \caption{Obtaining the 3D positions of the 2D-3D correspondences for use in projector calibration. (a) For each target location, a projector calibration image is acquired from the viewpoint of the `downwards-facing' camera, containing a projected asymmetric circle pattern at the target location and a chessboard pattern placed on the floor nearby. Circle pattern center points and chessboard corners detected automatically (overlain for illustration). (b) Given a projector calibration image, the scene plane is recovered in the coordinate frame of the camera (black with up vector red) via spatial resection with respect to 2D-3D correspondences obtained using the chessboard pattern (blue); the 3D positions of the 2D-3D correspondences to be used in calibrating the projector (red, in scene plane) are obtained by intersection with the scene plane of the back-projections (rays, likewise gray) of the 2D center points of the circle pattern detected in the image plane of the camera.} %The corresponding 2D positions are detected in the image of the asymmetric circles pattern image projected by the projector (not shown). The `downwards-facing' camera is shown relative to the scene plane in terms of its camera frustum (black, with up vector in red).
    \label{fig:2d}
\end{figure}

@@

\paragraph{Virtual projector} The placement of the virtual projector---for the recovered projector given a target location---determines from which pose the image to be projected is to \textit{appear} to have been projected.  We carry out this placement according to a small handful of steps. It is in accordance with the $X$- and $Y$-axes of the `downwards-facing' camera that we wish to place the $X$- and $Y$-axes of the augmentation, since we wish to intuitively be able to use the rotation of the camera relative to the scene plane to set those axes. It is, however, only if the virtual projector be placed to face the scene plane directly that the projection will appear free of distortions; this is noteworthy, since a physical camera placed to face downwards is almost certain to not face downwards to the scene plane precisely. Accordingly, we rotate the recovered camera about its center of projection to align its optical axis\footnote{Strictly speaking, the optical axis is the back-projection of the principal point; in our usage, we understand it to refer to the ray through center of the image plane.} with the normal vector of the scene plane by applying the minimum arc-length rotation that relates the two, giving a \textit{virtual} camera facing directly downwards to the scene plane (cf.\ Figure~\ref{fig:virtualcam}). To obtain the virtual projector, we then (i) intersect the scene plane with the optical axis of the projector and rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and (ii) align the $X$- and $Y$-axes with those of the virtual camera. Finally, we (iii) translate along the scene plane's normal, in order to satisfy the desired metric projected image dimensions; the height $h$ [m] above the ground plane at which the virtual projector is to be placed if the image---with original image width of $w_\text{im}$ [px]---is to be projected to the scene plane with a metric width of $w$ [m] is given by
\begin{equation}
h = w \times f_\text{proj} / w_\text{im},
\end{equation}
where $f_\text{proj}$ [px] is the focal length of the projector. These three steps are illustrated in Figure~\ref{fig:virtualproj}. The resulting virtual projector is thus rendered fronto-parallel with the scene plane---enabling projection to the scene plane absent of projective distortions---and projects to the scene plane in the desired scale and with the the $X$- and $Y$-axes of the augmentation set in accordance with those of the `downwards-facing' camera. %\footnote{A physical camera placed to face downwards is almost certain to not face downwards precisely; in contrast, we align the virtual camera's optical axis exactly with the scene plane's normal vector, rendering it genuinely fronto-parallel with respect to the scene plane.}

@@

\begin{figure}
    \centering
    \includegraphics[height=4.5cm]{images/hans_undist_.pdf}
    \caption{Projection of the warped image from Figure \ref{fig:warp}(a) to corresponding target location at the upper-right corner of the floorspace, acquired by the `downwards-facing' camera. Note that besides correcting for projective distortions, the warp places the axes of the augmentation in accordance with the axes of the `downwards-facing' camera, and that the dimensions of the augmentation are in line with the desired target dimensions (50~cm~$\times$~31.25~cm). To provide context, the corners of the full projected image extent are projected to the floor in light green (emphasized with overlain dashed circles).}
    \label{fig:final_proj}
\end{figure}

@@

\begin{figure}
    \centering
    \subfloat[\centering Hardware setup (projector, steerable mirror system, camera).]{{\includegraphics[height=4.75cm]{images/system3_.pdf}}}  %3.6
    \quad
    \subfloat[\centering Measurement for augmentation, using a steel rule and a digital angle gauge (enlargements on the right).]{{\includegraphics[height=4.75cm]{images/meas2_.pdf}}}
    \caption{Evaluation scenario. (a) Our hardware setup, comprised of a projector, a steerable mirror system, and a stereo camera, of which we used only the left view. (b) Example augmentation produced by projecting---to one of the 15 target locations across the floorspace considered in our evaluation, to the upper-left corner of our floorspace---an image warped using our approach. The digital angle gauge reads $89.6^\circ{}$ for the top-left corner, and the steel rule 49.9 cm for the bottom edge. Corners of the full projected image extent projected to the floor in light green to provide context. Note that blur has a minimal impact on the quality of the augmentation, and hence on the accuracy of the measurements.}
    \label{fig:eval}
\end{figure}

@@

\begin{table}[ht!]
\caption{Mean absolute error (MAE) and maximum absolute error in units of centimeters, with respect to the four sides (top, bottom, left, right) of the 15~augmentations produced using our approach for 15 target locations spread across the floorspace, respectively. Errors were computed against intended augmentation dimensions of 50~cm~$\times$~31.25~cm (i.e., 50~cm for top and bottom, 31.25~cm---rounded to 31.3~cm for the purposes of the computing the errors---for left and right).} %Note that absolute errors in no instance exceeded 1~cm for any side of any of the 15~augmentations.
\label{table:length}
\centering
{\small
\begin{tabularx}{7.4cm}{r p{1cm} p{1cm} p{1cm} p{1cm}}
\toprule
  & Top & Bottom & Left & Right \\
\midrule
MAE {\tiny[cm]} & 0.23 & 0.17 & 0.22 & 0.2 \\
%Min AE {\tiny[cm]} & 0.0 & 0.0 & 0.0 & 0.0 \\
Max AE {\tiny[cm]} & 0.8 & 0.6 & 0.5 & 0.5 \\
\bottomrule
\end{tabularx}}
\end{table}

@@

\begin{table}[ht!]
\caption{Mean absolute error (MAE) and maximum absolute error in units of degrees, with respect to the top-left and bottom-right corners of the 15~augmentations produced using our approach for 15 target locations spread across the floorspace, respectively. Errors computed in terms of deviation from $90^\circ{}$.}
\label{table:angle}
\centering
{\small
\begin{tabularx}{6.75cm}{r p{1.95cm} p{1.95cm}}
\toprule
  & Top Left & Bottom Right \\
\midrule
MAE {\tiny[deg]} & 0.17 & 0.32 \\
%Min AE {\tiny[deg]} & 0.0 & 0.0 \\
Max AE {\tiny[deg]} & 0.9 & 0.5 \\
\bottomrule
\end{tabularx}}
\end{table}
